Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-08 ms.tex
Updates from Overleaf

% Author: Matthew Turner

@@

Empirical research supports some of these theoretical predictions. Organisms flexibly use social learning as a function of the ambiguity of the environmental cue and of other environmental features that are often subsumed under the rubric of ``uncertainty.''
While some studies explicitly impose a cost whenever participants use asocial
information \cite{Morgan2012,atkisson_etal2012}, 
others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
For example, when participants received equivocal private information about the best investment to make in a lab game,
they were more likely to rely on social information to make their choice~\cite{Toelch2013}. 
\citeA{McElreath2005} developed a similar experiment where participants ``pulled'' virtual slot machine arms (often called ``bandits''), each yielding stochastic payoffs. Participants relied more on social learning when the bandits had higher-variance payoffs, and when the highest-paying bandit changed more frequently. 
The number of options to choose between can also increase uncertainty about the optimal choice, and has been shown to increase participants' reliance on social learning \cite{Muthukrishna2016a}.

@@

\bibliography{/Users/mt/workspace/Writing/library.bib}

>>>>

@@

Empirical research supports some of these theoretical predictions. Organisms flexibly use social learning as a function of the ambiguity of the environmental cue and of other environmental features that are often subsumed under the rubric of ``uncertainty.''
While some studies explicitly impose a cost whenever participants use asocial
information \cite{Morgan2012,Atkisson2012}, 
others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
For example, when participants received equivocal private information about the best investment to make in a lab game,
they were more likely to rely on social information to make their choice~\cite{Toelch2013}. 
\citeA{McElreath2005} developed a similar experiment where participants ``pulled'' virtual slot machine arms (often called ``bandits''), each yielding stochastic payoffs. Participants relied more on social learning when the bandits had higher-variance payoffs, and when the highest-paying bandit changed more frequently. 
The number of options to choose between can also increase uncertainty about the optimal choice, and has been shown to increase participants' reliance on social learning \cite{Muthukrishna2016a}.

@@

% \bibliography{/Users/mt/workspace/Writing/library.bib}
\bibliography{this.bib}
